---
title: "Data Visualization"
author: "Sorenson Impact Center Data Science Team"
date: "6/24/2019"
output: 
  ioslides_presentation:
    logo: newtemplate/SI_DESB_logo.png
    css: newtemplate/SI_styles.css
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
<script src="https://ajax.googleapis.com/ajax/libs/jquery/1.12.2/jquery.min.js"></script>

<script>
    $(document).ready(function() {
      $('slide:not(.title-slide, .backdrop, .segue)').append('<footer label=\"DRAFT: DO NOT CIRCULATE!\"></footer>');    
    })
</script>

<style>
  footer:after {
    content: attr(label);
    font-size: 12pt;
    position: absolute;
    bottom: 20px;
    left: 60px;
    line-height: 1.9;
  }
</style>




## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

