---
title: "Iteration"
author: "Daniel"
date: "July, 2018"
output:
  ioslides_presentation:
    css: template/SI_styles.css
    logo: template/SI_mobius_logo_large_white.png
    template: template/SI_ioslides.html
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(sorensonimpact)
library(nycflights13)
si_ggplot_theme_update()

flights <- flights
```


<!-- Go to: http://rmarkdown.rstudio.com/ioslides_presentation_format.html#overview for info on how to customize individual slides (centering, changing colors, etc).  I can also create custom css if we want a couple versions of slide templates that can be called from within this document. - Jon -->

<!-- The following is script for the footer. It must remain before the first slide: -->
<script src="https://ajax.googleapis.com/ajax/libs/jquery/1.12.2/jquery.min.js"></script>
<script>
    $(document).ready(function() {
    $('slide:not(.title-slide, .backdrop, .segue)').append('<footer></footer>');    
    $('footer').attr('label', 'Draft -- Do not circulate');
  })
</script>
<style>
  footer:after {
    font-size: 12pt;
    content: attr(label);
    position: absolute;
    margin-left: auto;
    margin-right: auto;
    left: 60px;
    right: 0;
    text-align:left;
    bottom: 20px;
    line-height: 1.9;
    display: block;
  }
</style>
<!-- End Footer -->

## Iteration

- One of the most valuable tools of computing
- Imperative vs. Functional

## Tibble

```{r}
df <- tibble(
  a = rnorm(10),
  b = rnorm(10),
  c = rnorm(10),
  d = rnorm(10)
) 

kable(df)

```


## The Hard Way

```{r, echo=T}
median(df$a)
median(df$b)
median(df$c)
median(df$d)
```


## The For Loop Way

```{r, echo=T}
output <- vector("double", ncol(df))  # 1. output

for (i in seq_along(df)) {            # 2. sequence
  output[[i]] <- median(df[[i]])      # 3. body
}

output
```


## The For Loop Way, Simplified

```{r, echo=T}

for (i in 1:5) {
  print(i)      
}

```


## The For Loop Way, Simplified

```{r, echo=T}
list_of_numbers <- c(1:5)

for (number in list_of_numbers) {
  print(number + 1)      
}

```


## The Nested For Loop

```{r, echo=T}

for (i in 1:5) {
  for (x in 1:5) {  
    print(i * x)
  }
}

```


## For Loop Tips

- Start by assigning "i" and testing
- with long loops, print(i) so you know where you are

## Exercise 1

- Print 1 - 100


## FizzBuzz

- Make a character vector of  length 100
- When the number is a multiple of 3 add “Fizz” instead of the number
- When the number is a multiple of 5 add “Buzz instead of the number
- When the number is a multiple of both add “FizzBuzz”


## Two Clues (But don't look down)

```{r, echo=T}
output <- vector("double", ncol(df))  # 1. output

for (i in seq_along(df)) {            # 2. sequence
  output[[i]] <- median(df[[i]])      # 3. body
}

# Modulo operation
15 %% 3 == 0

```


## if_else solution

```{r, echo=T}
output <- vector("character", 100)

for (i in seq_along(output)) {
  output[[i]] <- if_else(i %% 3 == 0 & i %% 5 == 0, "FizzBuzz",
                         if_else(i %% 3 == 0, "Fizz",
                                 if_else(i %% 5 == 0, "Buzz", as.character(i))))
}

output
```


## Case When Solution

```{r, echo=T}
output <- vector("character", 100)

for (i in seq_along(output)) {
  
  output[[i]] <- case_when(i %% 3 == 0 & i %% 5 == 0 ~ "FizzBuzz",
                           i %% 3 == 0 ~ "Fizz",
                           i %% 5 == 0 ~ "Buzz",
                           TRUE ~ as.character(i))
}

output
```


## While loop

```{r, echo=T}
i <- 1
j <- 5

while (i <= j) {
  # body
  i <- i + 1 
}

i
```


## Simulation

```{r, echo=T}
flip <- function() sample(c("T", "H"), 1)

flips <- 0
nheads <- 0

while (nheads < 3) {
  if (flip() == "H") {
    nheads <- nheads + 1
  } else {
    nheads <- 0
  }
  flips <- flips + 1
}
flips
```


## Motivating Examples

https://daniel-hadley.shinyapps.io/Recidivism_App/

https://github.com/DanielHadley/538_riddler


## Motivating Examples

```{r, echo=T, eval=F}
districts <- c("Nestucca", "Astoria", "Neah-Kah-Nie", "Seaside", "Tillamook", "Jewell", "Knappa", "Warrenton")

for (d in districts) {
  small_d_district <- d
  try(rmarkdown::render("~/Github/ADP_Oregon/2018May_Presentation.Rmd",
                        output_file = paste0(d, "_2018May_Presentation.html"), 
                        output_dir = "~/Github/ADP_Oregon/May_Reports/"))
  }
```


## Map

```{r, echo=T}
df %>% map(mean)
```


## Motivating Map

```{r, echo=T, eval=F}
sheets <- readxl::excel_sheets("~/NWORPSFeasibility_Astoria.xlsx")

clean_NWORPS <- function(x){
  test <- read_excel("~/NWORPSFeasibility_Astoria.xlsx", sheet = x) %>% 
    otherstuff()
}

NWORPS <- sheets %>% 
    map(clean_NWORPS) %>% 
  reduce(bind_rows)
```


## Function refresher

1.  You need to pick a __name__ for the function.

1.  You list the inputs, or __arguments__, to the function inside `function`.

1.  You place the code you have developed in __body__ of the function, a 
    `{` block that immediately follows `function(...)`.
 
    
## Function refresher

```{r, echo=T}
sum.of.squares <- function(x,y) {
  x^2 + y^2
}
```


## Final Exercise

- Make a FizzBuzz function
- Map it over a vector between 1 and 100
